High-order cognition is supported by complex but compressible brain activity patterns

### 2023-02-28 paper/main.tex
checking in results writeup for fig 3

\begin{figure}
  \centering

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/information_and_compression_over_time}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/decode_pcs_network}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/pca_neurosynth}

>>>>

\begin{figure}[tp]
  \centering

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.8\textwidth]{figs/information_and_compression_over_time}

@@

If informativeness (to the temporal decoders) and compressibility vary with the
cognitive richness of the stimulus, might these measures also vary over time
\textit{within} a given condition? For example, participants in the intact
condition might process the ongoing story more deeply later on in the story
(compared with earlier in the story) given the additional narrative background
and context they had been exposed to by that point. To examine this
possibility, we divided each condition into three successive time segments. We
computed decoding curves (Fig.~\ref{fig:inflection-thirds}A) and inflection
points (Fig.~\ref{fig:inflection-thirds}B) for each segment and condition. We
found that, in the two most cognitively rich conditions (intact and paragraph),
both decoding accuracy and compressibility, as reflected by the change in
decoding curves, increased with listening time (intact: $t(XXX) = XXX, p =
XXX$; paragraph: $t(XXX) = XXX, p = XXX$). These changes may reflect an
increase in comprehension or depth of processing with listening time. In
contrast, the decoding accuracy and compressibility \textit{decreased} with
listening time in the word condition ($t(XXX) = XXX, p = XXX$) and rest
condition ($t(XXX) = XXX, p = XXX$). This might reflect the depletion of
attentional resources in the less-engaging word and rest conditions.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/decode_pcs_network}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/pca_neurosynth}
